A community-maintained standard library of population genetic models

### 2020-05-01 popSimManu.tex
adjustment to intro para

\paragraph{The \stdpopsim library.}
The first contribution of the PopSim consortium is \stdpopsim, a
community-maintained library of empirical genome data and population genetics simulation
models. Figure \ref{fig:cartoon} shows a graphical
representation of the structure of \stdpopsim. The package centers
on a catalog of species (Fig.~\ref{fig:cartoon}A), 
and software resources to facilitate efficient simulations (Fig.~\ref{fig:cartoon}B-C).

>>>>

The first contribution of the PopSim consortium is \stdpopsim,
a community-maintained library of empirical genome data and population genetics simulation models.
Figure \ref{fig:cartoon} shows a graphical representation of the structure of \stdpopsim.
The package centers on a catalog of genomic information and demographic models
for a growing list of taxa (Fig.~\ref{fig:cartoon}A), 
and software resources to facilitate efficient simulations (Fig.~\ref{fig:cartoon}B-C).
